Summary of tumor cell classification with `AUCell` for `r params$library_id`

### 2024-07-12 analyses/cell-type-ewings/template_notebooks/auc-workflow/01-auc-results.Rmd
use number of genes detected and change output file name

---
title: "Summary of tumor cell classification with `AUCell` for `r params$library_id`"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  library_id: NULL
  sce_file: NULL
  aucell_results_file: NULL
  ref_auc_results: NULL
  geneset_scores_file: NULL
  marker_genes_file: NULL
  output_file: NULL
  auc_threshold: NULL
---

@@

```{r}
# add marker gene classification based on expression of at least 1 marker gene  
marker_gene_class_df <- markers_df |> 
  dplyr::select(barcodes, sum_raw_exp) |> 
  dplyr::distinct() |> 
  dplyr::mutate(
    marker_gene_classification = dplyr::if_else(
      sum_raw_exp > 0,
      "Tumor",
      "Normal"

@@

```{r}
classification_df |> 
  dplyr::filter(method == "marker_gene_classification") |> 
  dplyr::select(barcodes, marker_gene_classification = classification) |> 
  readr::write_tsv(params$output_file)
```

>>>>

---
title: "Summary of tumor cell classification with `AUCell` for `r params$library_id`"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  library_id: NULL
  sce_file: NULL
  aucell_results_file: NULL
  ref_auc_results: NULL
  geneset_scores_file: NULL
  marker_genes_file: NULL
  marker_class_file: NULL
  auc_threshold: NULL
  marker_threshold: 1
---

@@

```{r}
# get a list of tumor cells based on those that have number of marker genes expressed 
# greater than the threshold 
tumor_cells <- markers_df |> 
  dplyr::mutate(gene_detected = dplyr:if_else(gene_expression > 0 , 1, 0)) |> 
  dplyr::group_by(barcodes) |> 
  dplyr::summarize(total_genes = sum(gene_detected)) |> 
  dplyr::filter(total_genes >= params$marker_threshold) |> 
  dplyr::pull(barcodes)

# create a data frame with raw exp and classification 
# will add this to the larger data frame
marker_gene_class_df <- markers_df |> 
  dplyr::select(barcodes, sum_raw_exp) |> 
  dplyr::distinct() |> 
  dplyr::mutate(
    marker_gene_classification = dplyr::if_else(
      barcodes %in% tumor_cells,
      "Tumor",
      "Normal"

@@

```{r}
classification_df |> 
  dplyr::filter(method == "marker_gene_classification") |> 
  dplyr::select(barcodes, marker_gene_classification = classification) |> 
  readr::write_tsv(params$marker_class_file)
```
